---
title: "ffiec"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ffiec}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
no_creds <- ffiec::no_creds_available()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = !no_creds
)
```

```{r eval = no_creds, echo = FALSE, comment = NA}
message("No FFIEC API credentials available. Code chunks will not be evaluated.")
```

```{r setup}
library(ffiec)
```

## Using {ffiec}

This package attempts to offer a convenient interface to interact with the Central Data Repository 'REST API' service made available by the United States Federal Financial Institutions Examination Council ('FFIEC').

## Getting Started

If you haven't done so already, install {ffiec} and create an account through the FFIEC's Web Service portal using the instructions in the [README section](https://ketchbrookanalytics.github.io/ffiec/#installation).

With your username and password from the FFIEC's Web Service portal in-hand (either stored as environment variables or ready to be passed as function arguments), load the package using `library()`.

```{r load, eval = FALSE}
library(ffiec)
```

While the package offers several functions to enable different workflows and analyses, one general workflow is as follows:

- Collect a list of available Call reporting periods
- For each desired Call reporting period and desired Institution ID, retrieve Call report data

First, to obtain the available Call reporting periods, use the `get_reporting_periods()` function. The `as_data_frame` argument is set to `TRUE` to alter the return behavior of the function. By default, the function will return a list object.

```{r periods}
reporting_periods <- get_reporting_periods(as_data_frame = TRUE)
```

Next, filter the `get_reporting_periods()` return value to the period(s) of interest. For the purposes of this example, the four reporting periods in calendar year 2025 will be used.

```{r last_four_quarters}
reports_2025 <- reporting_periods |>
  dplyr::filter(ReportingPeriod <= as.Date("2025-12-31")) |>
  dplyr::slice_max(
    n = 4,
    order_by = ReportingPeriod
  ) |>
  dplyr::pull()
```

Using the `get_facsimile()` function, Call report data can be collected for the selected reporting periods and one or more specified institutions.

```{r call_data}
call_df <- get_facsimile(
  reporting_period_end_date = reports_2025,
  fi_id = c(480228, 451965)
)
```

Notice that each institution ID (column `BankRSSDIdentifier`) contains Call report data for each reporting period.

```{r call_data_count}
call_df |>
  dplyr::count(CallDate, BankRSSDIdentifier)
```

This example can be extended by comparing Call report values, either between periods or between institutions (or both). Below, the Call report data is filtered to display Tier 1 capital for each institution over the selected reporting periods.

```{r call_data_filter}
call_df |>
  dplyr::filter(MDRM == "RCFA8274") |>  # Tier 1 capital
  dplyr::mutate(Value = as.numeric(Value))
```

## Additional Uses
The package offers functions to interact with both Call report data and Uniform Bank Performance Report (UBPR) data.

To interact with the latter, simply substitute `get_ubpr_reporting_periods()` and `get_ubpr_facsimile()` into the above examples. However, please be aware that `get_ubpr_facsimile()` returns different column names than `get_facsimile()`.